Exceedance probability comparison for the simplified Naomi model

### 2023-06-16 src/naomi-simple_exceedance/exceedance.Rmd
Save exceedance probability output and put into poster #36
Create manuscript ready plot for exceedance, general plot improvements, and rerun report

plot1 <- ggplot(df_wide_second90, aes(x = tmbstan, y = TMB)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  labs(title = "Probability of 81% ART coverage in strata") +
  theme_minimal()

plot2 <- ggplot(df_wide_second90, aes(x = tmbstan, y = aghq)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  theme_minimal()

@@

plot1 <- ggplot(df_wide_second90, aes(x = tmbstan, y = TMB, col = sex)) +
  geom_point(alpha = 0.3) +
  scale_color_manual(values = c("#E69F00", "#F0E442")) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  labs(title = "Probability of at least 81% ART coverage in strata", col = "Sex") +
  theme_minimal() +
  theme(legend.position = "bottom")

plot2 <- ggplot(df_wide_second90, aes(x = tmbstan, y = aghq, col = sex)) +
  geom_point(alpha = 0.3) +
  scale_color_manual(values = c("#E69F00", "#F0E442")) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  guides(col = "none") +
  theme_minimal()

@@

plot1 <- ggplot(df_wide_1inc, aes(x = tmbstan, y = TMB)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  labs(title = "Probability of at least 1% incidence in strata") +
  theme_minimal()

plot2 <- ggplot(df_wide_1inc, aes(x = tmbstan, y = aghq)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  theme_minimal()

@@

>>>>

plot1 <- ggplot(df_wide_second90, aes(x = tmbstan, y = TMB)) +
  geom_point(shape = 1, alpha = 0.6, col = "#999999") +
  coord_fixed(ratio = 1) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  labs(x = "NUTS", y = "TMB") +
  theme_minimal()

plot2 <- ggplot(df_wide_second90, aes(x = tmbstan, y = aghq)) +
  geom_point(shape = 1, alpha = 0.6, col = "#999999") +
  coord_fixed(ratio = 1) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  labs(x = "NUTS", y = "PCA-AGHQ") +
  theme_minimal()

@@

plot1 <- ggplot(df_wide_second90, aes(x = tmbstan, y = TMB, col = sex)) +
  geom_point(shape = 1, alpha = 0.6) +
  coord_fixed(ratio = 1) +
  scale_color_manual(values = c("#E69F00", "#999999")) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  labs(col = "Sex") +
  guides(col = "none") +
  labs(x = "NUTS", y = "TMB") +
  theme_minimal()

plot2 <- ggplot(df_wide_second90, aes(x = tmbstan, y = aghq, col = sex)) +
  geom_point(shape = 1, alpha = 0.6) +
  coord_fixed(ratio = 1) +
  scale_colour_manual(values = c("#E69F00", "#999999"), labels = c("Female", "Male")) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  labs(x = "NUTS", y = "PCA-AGHQ", col = "Sex") +
  theme_minimal()

ggsave("second90.png", plot1 + plot2, h = 4, w = 6.25)

@@

df_wide_1inc <- df_wide_1inc %>%
  left_join(
    mf_out_fine %>%
      tibble::rowid_to_column("index"),
    by = "index"
  )

plot1 <- ggplot(df_wide_1inc, aes(x = tmbstan, y = TMB)) +
  geom_point(shape = 1, alpha = 0.6, col = "#999999") +
  coord_fixed(ratio = 1) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  labs(x = "NUTS", y = "TMB") +
  theme_minimal()

plot2 <- ggplot(df_wide_1inc, aes(x = tmbstan, y = aghq)) +
  geom_point(shape = 1, alpha = 0.6, col = "#999999") +
  coord_fixed(ratio = 1) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  labs(x = "NUTS", y = "PCA-AGHQ") +
  theme_minimal()

ggsave("1inc.png", plot1 + plot2, h = 4, w = 6.25)

@@

# Plot for manuscript

Combine the above plots into one nice one.
ABF (always be facetting):

```{r}
df_wide <- bind_rows(
  df_wide_second90 %>%
    mutate(type = "Second 90"),
  df_wide_1inc %>%
    mutate(type = "High incidence")
)

write_csv(df_wide, "exceedance.csv")

fct_reorg <- function(fac, ...) {
  fct_recode(fct_relevel(fac, ...), ...)
}

exceedance_manuscript_plot <- df_wide %>%
  pivot_longer(cols = c("TMB", "aghq"), names_to = "method", values_to = "estimate") %>%
  mutate(
    method = fct_reorg(method, "TMB" = "TMB", "PCA-AGHQ" = "aghq"),
    type = fct_relevel(type, "Second 90", "High incidence")
  ) %>%
  ggplot(aes(x = tmbstan, y = estimate, col = sex)) +
    geom_point(shape = 1, alpha = 0.6) +
    coord_fixed(ratio = 1) +
    scale_colour_manual(values = c("#56B4E9", "#999999"), labels = c("Female", "Male")) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    facet_grid(type ~ method) +
    labs(x = "", y = "", col = "Sex") +
    theme_minimal() +
    theme(
      legend.position = "bottom"
    )

exceedance_manuscript_plot

ggsave("exceedance.png", exceedance_manuscript_plot, h = 6.5, w = 6.25, bg = "white")
```
